Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2024-11-04 Paper.tex
refactor: clearer sentence
Fix transactions typo (#919)

\subsection{Execution}
\hypertarget{intrinsic_gas_g_0}{}We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_{\mathbf{i}}, T_{\mathbf{d}}} \begin{cases} \hyperlink{G__txdatazero}{G_{\mathrm{txdatazero}}} & \text{if} \quad i = 0 \\ \hyperlink{G__txdatanonzero}{G_{\mathrm{txdatanonzero}}} & \text{otherwise} \end{cases} \\
\nonumber {} & + \begin{cases} \hyperlink{G__txcreate}{G_{\mathrm{txcreate}}} + \hyperlink{initcode_cost}{R({\lVert T_{\mathbf{i}} \rVert})} & \text{if} \quad T_{\mathrm{t}} = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
\nonumber {} & + \hyperlink{G__transaction}{G_{\mathrm{transaction}}} \\
\nonumber {} & + \sum_{j = 0}^{\lVert T_{\mathbf{A}} \rVert - 1} \big( G_{\mathrm{accesslistaddress}} + \lVert T_{\mathbf{A}}[j]_{\mathbf{s}} \rVert G_{\mathrm{accessliststorage}} \big)
\end{align}
where $T_{\mathbf{i}},T_{\mathbf{d}}$ means the series of bytes of the transaction's associated data and initialisation EVM-code, depending on whether the transaction is for contract-creation or message-call.
$G_{\mathrm{txcreate}}$ is added if the transaction is contract-creating, but not if it is a result of EVM-code.
$\hyperlink{G__accesslistaddress}{G_{\mathrm{accesslistaddress}}}$ and $\hyperlink{G__accessliststorage}{G_{\mathrm{accessliststorage}}}$ are the costs of warming up account and storage access, respectively.
$G$ is fully defined in Appendix \ref{app:fees}.

@@

\hyperlink{T__r_T__s}{Reiterating from previously}:
\begin{eqnarray}
\linkdest{T__r}{T_{\mathrm{r}}} = \hyperlink{r}{r}\\
\linkdest{T__s}{T_{\mathrm{s}}} = \hyperlink{s}{s}
\end{eqnarray}
and $\hyperlink{T__w}{T_{\mathrm{w}}}$ of legacy transcations is either $27 + T_{\mathrm{y}}$ or $2\hyperlink{chain_id}{\beta} + 35 + T_{\mathrm{y}}$.

>>>>

\subsection{Execution}
\hypertarget{intrinsic_gas_g_0}{}We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_{\mathbf{i}}, T_{\mathbf{d}}} \begin{cases} \hyperlink{G__txdatazero}{G_{\mathrm{txdatazero}}} & \text{if} \quad i = 0 \\ \hyperlink{G__txdatanonzero}{G_{\mathrm{txdatanonzero}}} & \text{otherwise} \end{cases} \\
\nonumber {} & + \begin{cases} \hyperlink{G__txcreate}{G_{\mathrm{txcreate}}} + \hyperlink{initcode_cost}{R({\lVert T_{\mathbf{i}} \rVert})} & \text{if} \quad T_{\mathrm{t}} = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
\nonumber {} & + \hyperlink{G__transaction}{G_{\mathrm{transaction}}} \\
\nonumber {} & + \sum_{j = 0}^{\lVert T_{\mathbf{A}} \rVert - 1} \big( G_{\mathrm{accesslistaddress}} + \lVert T_{\mathbf{A}}[j]_{\mathbf{s}} \rVert G_{\mathrm{accessliststorage}} \big)
\end{align}
where $T_{\mathbf{i}},T_{\mathbf{d}}$ means the series of bytes of the transaction's associated data and initialisation EVM-code, depending on whether the transaction is for contract-creation or message-call.
$G_{\mathrm{txcreate}}$ is added if the transaction is contract-creating, but not if it is a message call.
$\hyperlink{G__accesslistaddress}{G_{\mathrm{accesslistaddress}}}$ and $\hyperlink{G__accessliststorage}{G_{\mathrm{accessliststorage}}}$ are the costs of warming up account and storage access, respectively.
$G$ is fully defined in Appendix \ref{app:fees}.

@@

\hyperlink{T__r_T__s}{Reiterating from previously}:
\begin{eqnarray}
\linkdest{T__r}{T_{\mathrm{r}}} = \hyperlink{r}{r}\\
\linkdest{T__s}{T_{\mathrm{s}}} = \hyperlink{s}{s}
\end{eqnarray}
and $\hyperlink{T__w}{T_{\mathrm{w}}}$ of legacy transactions is either $27 + T_{\mathrm{y}}$ or $2\hyperlink{chain_id}{\beta} + 35 + T_{\mathrm{y}}$.
